---
title: "README"
author: "Martin Raubenheimer"
date: "2026-06-18"
output: github_document
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup2, include=FALSE}
gc()
rm(list =ls())

library(tidyverse)

Baby_Names <- read_rds("data/US_Baby_names/Baby_Names_By_US_State.rds") %>%
    rename_with(tolower) %>%
    mutate(name = str_to_title(name), gender = toupper(gender))

 national_names <- Baby_Names %>%  
        group_by(name, year, gender)

hbo_titles <- read_rds("data/US_Baby_names//HBO_titles.rds") %>%  rename_with(tolower) 

hbo_credits <- read_rds("data/US_Baby_names//HBO_credits.rds")  %>%
  mutate(across(where(is.character), ~ iconv(., to = "UTF-8", sub = "byte")))%>%
    rename_with(tolower)

hbo <- left_join(hbo_credits,hbo_titles, "id") %>% 
         select(-c(imdb_votes, tmdb_score,role, age_certification,runtime, imdb_id))

charts <- read_rds("data/US_Baby_names/charts.rds") %>% 
       rename_with(~ tolower(gsub("[ -]", "_", .x))) %>%
       mutate(date = as_date(date), year = year(date))

list.files('Question2/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse)
```

# 24954578
 
# Question 2

## Introduction

## Persistence analysis
```{r}
run_persistence_analysis(Baby_Names)
```


## Popularity surges

```{r}

my_static_plot <- build_pop_culture_plot(Baby_Names, charts, hbo)
# Render it interactively
interactive_plot <- ggplotly(my_static_plot, tooltip = "text")
interactive_plot

```

-I took the Billboard and HBO datasets and extracted exactly one critical year for each artist or character. For Billboard, we grouped the data by artist and extracted the earliest year they hit their absolute highest chart rank. This gave us a clean lookup table of "Pop Culture Catalysts" and the year they occurred.

- I then looked at the baby names. Instead of just looking at raw numbers, the code used the lag() function to calculate the Year-over-Year (YoY) percentage growth for every single name.

  - If a name grew by 5% or 10%, the algorithm ignored it.
  - If a name grew by >100% in a single year (and had at least 100 births to filter out statistical noise from rare names), the algorithm flagged that specific year as a "Spike."
  
- Finally, the code joined the baby name data with the Event Ledger. It asked a specific question: Did this detected baby-name spike happen in the exact same year, or up to two years after, the artist/character peaked in the ledger?

If yes, the code assigned it a Red or Blue color.
If no, it remained Grey.


# Density
```{r}
famous_names <- c("Miley", "Billie", "Drake", "Rihanna", "Mariah", "Arya", "Zendaya", "Khaleesi")

fame_plot <- plot_fame_density(Baby_Names, charts, hbo, famous_names)

fame_plot
```

# Genres
```{r}
hbo_genres_plot <- plot_hbo_genres(Baby_Names, hbo)

hbo_genres_plot
```

