---
title: "baby_names_pdf"
output: pdf_document
date: "2026-06-19"
---




```{r setup, include=FALSE}
gc()
rm(list =ls())

knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)

# 1. SET THE TOOLBOX FIRST
.libPaths("C:/R-local-libs")
pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse, pagedown, bookdown)

# 2. SET THE DESK TO QUESTION 2
knitr::opts_knit$set(root.dir = "C:/datsci exam 1/24954578/Question2")
setwd("C:/datsci exam 1/24954578/Question2")


# 3. LOAD DATA USING CLEAN RELATIVE PATHS
Baby_Names <- read_rds("data/US_Baby_names/Baby_Names_By_US_State.rds") %>%
    rename_with(tolower) %>%
    mutate(name = str_to_title(name), gender = toupper(gender))

national_names <- Baby_Names %>%  
        group_by(name, year, gender)

hbo_titles <- read_rds("data/US_Baby_names/HBO_titles.rds") %>%  
    rename_with(tolower) 

hbo_credits <- read_rds("data/US_Baby_names/HBO_credits.rds")  %>%
    mutate(across(where(is.character), ~ iconv(., to = "UTF-8", sub = "byte"))) %>%
    rename_with(tolower)

hbo <- left_join(hbo_credits, hbo_titles, "id") %>% 
         select(-c(imdb_votes, tmdb_score, role, age_certification, runtime, imdb_id))

charts <- read_rds("data/US_Baby_names/charts.rds") %>% 
       rename_with(~ tolower(gsub("[ -]", "_", .x))) %>%
       mutate(date = as_date(date), year = year(date))

# 4. SOURCE SCRIPTS
list.files("code/", full.names = TRUE, recursive = TRUE) %>% 
    as.list() %>% 
    walk(~source(.))


```

\newpage

# Introduction

# Persistence analysis
```{r}
persistence_plot <- run_persistence_analysis(Baby_Names)
persistence_plot
```

# Popularity surges

```{r}

my_static_plot <- build_pop_culture_plot(Baby_Names, charts, hbo)

```
 This plot shows the names for which the year-on-year growth has doubled.
 An observation is coloured red if the name  doubled in a two range of the release rate of a tv show or movie and in coloured blue if the name doubled in the a two range since a artist reached there best position on the Top 100. This clearly illustrates how quickly pop culture affects Baby_Names. Looking at the left-bottom we see Zendaya is name that has grown and has played in many movies recently.


# Density
```{r}
famous_names <- c("Miley", "Billie", "Drake", "Rihanna", "Mariah", "Arya", "Zendaya", "Khaleesi")

fame_plot <- plot_fame_density(Baby_Names, charts, hbo, famous_names)

fame_plot
```

# Genres
```{r}
hbo_genres_plot <- plot_hbo_genres(Baby_Names, hbo)

hbo_genres_plot
```


