---
title: "Question3"
author: "Martin Raubenheimer"
date: "2026-06-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
loan <- readRDS("data/Loan_Cred/loan_data.rds")
dictionary <- read_xlsx("data/Loan_Cred/Dictionary.xlsx")

# Source functions

list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

d <- loan_col_select("data/Loan_Cred/loan_data.rds")
```

I wanted to generate a function that illustrates the differences in POD for home owners and non-home owners, and young people versus old.

- different categories easily illustrate differences as well as different bars for home owners

- filtered for short-term loans
```{r}
emp_length_bar(d)
```
This graphs tells us two different stories.
1. That home owners tend to have lower default rates than non-homers.
2. This gap actually increases as people have been longer employed.
The lowest default rate seems to be people who have been employed between 6 and 8 years and owns a home.

```{r}
# Plot 1: Y-axis is Interest Rate
plot_interest <- credit_grade_y(
  data = d, 
  y_var = "int_rate", 
  plot_title = "Average Interest Rate by Credit Grade",
  plot_subtitle = "Segmented by Credit Age Profile",
  plot_ylab = "Average Interest Rate (%)"
)
```
```{r}

# Plot 2: Y-axis is Defaults
# (Assuming you created the `is_default` binary column in your master data beforehand)
plot_defaults <- credit_grade_y(
  data = d %>%
    mutate(is_default = ifelse(loan_status %in% c("Charged Off", "Default"), 1, 0)), 
  y_var = "is_default", 
  plot_title = "Default Rate by Credit Grade",
  plot_subtitle = "Segmented by Credit Age Profile",
  plot_ylab = "Default Rate"
)
```

