---
title: "Question4"
author: "Martin Raubenheimer"
date: "2026-06-18"
output: html_document
---
```{r}
library(tidyverse)

source("code/clean_csv_import.R")
net_mov <- clean_csv_import("data/netflix/netflix_movies.csv")
credits <- readRDS("data/netflix/credits.rds")
titles <- readRDS("data/netflix/titles.rds")


net_d <- titles %>%
  left_join(net_mov, by = "title") %>%
  left_join(credits, by = "id")

```

## Do people like long movies
I was interested whether, there was clear universal preferences for length.
It is very clear from the plot that the highest ratings go to shows that only steal an hour of someone's day/


- The function filters the titles dataset to keep rows with non-missing IMDb scores and runtimes within the 7.0–10.0 range, then creates rating_band by grouping scores into 0.5-point intervals using cut().

-It plots a boxplot showing runtime distribution for each rating band using ggplot2, with viridis colors for fills, a minimal theme, and hides outlier points at 40% transparency.
```{r}
plot_runtime_by_rating_band(net_d, breaks = seq(7, 10, by = 0.5))


```

